---
title: "RBayesflow Phase 2: Prior Specification and Prior Predictive Simulation"
format: html
params:
  mode: "learn"
  stage: "explore"
---

<!--
# POSIT ASSISTANT CONTEXT
# This is Phase 2 of the RBayesflow Bayesian workflow.
# Current mode: set by params$mode | Current stage: set by params$stage
# Read wf_context.json in the project root for full workflow state.
# Do NOT suggest running any code directly. Always present suggestions
# as non-executable previews. The user is specifying priors and running
# prior predictive simulation BEFORE fitting any model to data.
-->

## Setup

```{r setup, message=FALSE}
source("R/source_all.R")
wf <- readRDS("wf_phase1.rds")   # Load wf from Phase 1
```

## Prior Specification

Edit the priors below to reflect your domain knowledge.

```{r set-priors}
library(lme4)
library(brms)
data <- sleepstudy

formula <- Reaction ~ Days + (Days | Subject)
family  <- gaussian()

# Specify your priors here. Each prior() call names a parameter class.
# See ?brms::set_prior for syntax.
priors <- c(
  prior(normal(250, 50), class = Intercept),
  prior(normal(10, 5),   class = b, coef = Days),
  prior(exponential(1),  class = sigma)
)
```

::: {.callout-tip}
**Posit Assistant:** Ask "Are these priors reasonable for reaction
time data measured in milliseconds?" to get a domain-specific
assessment of prior scale.
:::

## Phase 2: Prior Predictive Simulation

Run this chunk to simulate from the prior before seeing the data.
This may take 1–2 minutes.

```{r phase2, eval=FALSE}
wf <- run_phase2(
  wf      = wf,
  formula = formula,
  family  = family,
  priors  = priors,
  data    = data,
  seed    = 42
)
```

::: {.callout-note}
**Learn mode:** The prior predictive plot shows what data values
your priors consider plausible before seeing any observations.
Reaction times below 0 ms or above 5000 ms are implausible — if
your prior predictive draws include many such values, tighten your
priors.
:::

## Save workflow state

```{r save-wf, eval=FALSE}
saveRDS(wf, "wf_phase2.rds")
cat("Phase 2 complete. wf saved to wf_phase2.rds\n")
cat("Proceed to templates/phase3_fit.qmd\n")
```
