---
title: "RBayesflow Phase 3: Model Fitting"
format: html
params:
  mode: "learn"
  stage: "explore"
---

<!--
# POSIT ASSISTANT CONTEXT
# This is Phase 3 of the RBayesflow Bayesian workflow.
# Current mode: set by params$mode | Current stage: set by params$stage
# Read wf_context.json in the project root for full workflow state.
# Do NOT suggest running any code directly. Always present suggestions
# as non-executable previews. The user is fitting a model via brms
# with cmdstanr backend. Do not display coefficient summaries until
# Phase 4 diagnostics confirm wf_state$diagnostics$passed == TRUE.
-->

## Setup

```{r setup, message=FALSE}
source("R/source_all.R")
wf <- readRDS("wf_phase2.rds")   # Load wf from Phase 2
```

## Model specification

Review the formula and family carried forward from Phase 2.

```{r model-spec}
library(lme4)
library(brms)
data <- sleepstudy

# These should match Phase 2 — edit only if your model has changed.
formula <- Reaction ~ Days + (Days | Subject)
family  <- gaussian()
priors  <- wf$priors_objects[[1]]   # Priors stored in Phase 2
```

## Phase 3: Model Fitting

Run this chunk to fit the model. This may take 5–15 minutes.

```{r phase3, eval=FALSE}
result <- run_phase3(
  wf      = wf,
  formula = formula,
  data    = data,
  family  = family,
  priors  = priors,
  seed    = 42,
  chains  = 4,
  iter    = 2000,
  warmup  = 1000,
  refresh = 100
)
wf  <- result$wf
fit <- result$fit
```

::: {.callout-note}
**Parameterization note:** After fitting, `wf$parameterization`
records whether brms used a centered or non-centered parameterization
for any random effects. If you see divergent transitions in Phase 4,
call `refit_noncentered(wf, fit)` to switch automatically.
:::

## Save workflow state and fit

```{r save-wf, eval=FALSE}
saveRDS(fit, "fit.rds")
saveRDS(wf,  "wf_phase3.rds")
cat("Phase 3 complete.\n")
cat("fit saved to fit.rds | wf saved to wf_phase3.rds\n")
cat("Proceed to templates/phase4_diagnostics.qmd\n")
```
