---
title: "RBayesflow Phase 6: Model Comparison (LOO-CV)"
format: html
params:
  mode: "learn"
  stage: "explore"
---

<!--
# POSIT ASSISTANT CONTEXT
# This is Phase 6 of the RBayesflow Bayesian workflow.
# Current mode: set by params$mode | Current stage: set by params$stage
# Read wf_context.json in the project root for full workflow state.
# Do NOT suggest running any code directly. Always present suggestions
# as non-executable previews.
# The user is running LOO-CV (leave-one-out cross-validation) for model
# comparison. In learn mode: ask the user what the elpd_diff and se_diff
# values tell them about the models, citing Vehtari et al. (2017).
# In practice mode: display the LOO comparison table directly.
-->

## Setup

```{r setup, message=FALSE}
source("R/source_all.R")
library(loo)
wf  <- readRDS("wf_phase5.rds")
fit <- readRDS("fit.rds")
```

## Phase 6: LOO-CV Model Comparison

Compute LOO for the current model. If comparing multiple models, load
each fitted model and run `loo_compare()`.

```{r loo-single, eval=FALSE}
# LOO for the current model
loo_fit <- loo(fit)
print(loo_fit)
```

```{r loo-compare, eval=FALSE}
# Comparing two models: load a second fit and compare
# fit2 <- readRDS("fit2.rds")
# loo_fit2 <- loo(fit2)
# loo_compare(loo_fit, loo_fit2)
```

::: {.callout-note}
**Learn mode — interpreting LOO output:**
The key column is `elpd_loo` (expected log predictive density). Higher
(less negative) values indicate better out-of-sample predictive
accuracy. When comparing models with `loo_compare()`, the `elpd_diff`
column shows how much better or worse each model is relative to the
top model; values more negative than `-2 * se_diff` indicate a
meaningful difference. See Vehtari, Gelman & Gabry (2017),
*Practical Bayesian model evaluation using leave-one-out
cross-validation and WAIC*, for detailed guidance.

**Posit Assistant:** Ask "My elpd_diff is -4.2 with se_diff of 3.1 —
is this a meaningful difference between the models?" for a Socratic
interpretation.
:::

## Update workflow state

```{r update-wf, eval=FALSE}
wf$loo_complete <- TRUE
wf$loo_table    <- as.data.frame(loo_fit$estimates)
export_context(wf)
saveRDS(wf, "wf_phase6.rds")
cat("Phase 6 complete. wf saved to wf_phase6.rds\n")
cat("Proceed to templates/bayesflow_report.qmd to render your report.\n")
```
