---
title: "RBayesflow Phase 1: Data Inspection and Goal Declaration"
format: html
params:
  mode: "learn"
  stage: "explore"
---

```{=html}
<!--
# POSIT ASSISTANT CONTEXT
# This is Phase 1 of the RBayesflow Bayesian workflow.
# Current mode: set by params$mode | Current stage: set by params$stage
# Read wf_context.json in the project root for full workflow state.
# Do NOT suggest running any code directly. Always present suggestions
# as non-executable previews. The user is declaring their scientific
# goal and inspecting data before any model is fitted.
-->
```

## Setup

Run this chunk interactively in RStudio (Ctrl+Enter). Do not render this file — use it as an interactive script.

```{r setup, message=FALSE}
source("R/source_all.R")
wf <- init_workflow(mode = params$mode, stage = params$stage)
```

## Load your data

If you have real data to load, replace the example below. For a simulated-data analysis (where data is generated in code), set `simulated <- TRUE` and skip to the next chunk.

```{r load-data}
# Set simulated <- TRUE if your data is generated programmatically.
# Set simulated <- FALSE and load your data below if working with a real dataset.
simulated <- FALSE

# If simulated <- FALSE, replace this with your own data-loading code:
# data <- read.csv("path/to/your/data.csv")
# For demonstration, we use the sleepstudy dataset:
library(lme4)
data <- sleepstudy
outcome_var  <- "Reaction"
outcome_type <- "continuous"
goal         <- "Estimate the effect of sleep deprivation on reaction time"
```

## Phase 1: Data Inspection and Off-Ramp Assessment

Run this chunk to inspect your data and see available analysis paths.

```{r phase1, eval=FALSE}
wf <- run_phase1(
  wf           = wf,
  data         = if (simulated) NULL else data,
  outcome_var  = if (simulated) NULL else outcome_var,
  outcome_type = if (simulated) NULL else outcome_type,
  goal         = if (simulated) NULL else goal,
  simulated    = simulated
)
```

::: callout-note
**Interactive step required:** The chunk above uses `readline()` to ask you to select an analysis path. Run it in the RStudio Console, not by rendering. Type the number of your chosen path and press Enter.
:::

## Off-Ramp Decision

If you selected a non-Bayesian path, use `exit_workflow()` now:

```{r exit-optional, eval=FALSE}
# Only run this if you chose a non-Bayesian analysis path above.
# Replace "your_chosen_method" with the method string shown in the off-ramp output.
wf <- exit_workflow(
  wf           = wf,
  method       = "your_chosen_method",
  alternatives = c("logistic_bootstrap", "full_stan")
)
```

## Save workflow state

```{r save-wf, eval=FALSE}
saveRDS(wf, "wf_phase1.rds")
cat("Phase 1 complete. wf saved to wf_phase1.rds\n")
cat("Proceed to templates/phase2_priors.qmd\n")
```
