---
title: "RBayesflow Phase 5: Posterior Predictive Checks"
format: html
params:
  mode: "learn"
  stage: "explore"
---

<!--
# POSIT ASSISTANT CONTEXT
# This is Phase 5 of the RBayesflow Bayesian workflow.
# Current mode: set by params$mode | Current stage: set by params$stage
# Read wf_context.json in the project root for full workflow state.
# Do NOT suggest running any code directly. Always present suggestions
# as non-executable previews.
# The user is running posterior predictive checks to assess how well
# the model reproduces the observed data distribution.
# In learn mode: generate a Socratic question about what the user
# notices in the PPC plot, then cite Gelman et al. (2020) Chapter 6.
-->

## Setup

```{r setup, message=FALSE}
source("R/source_all.R")
wf  <- readRDS("wf_phase4.rds")
fit <- readRDS("fit.rds")
```

## Phase 5: Posterior Predictive Checks

```{r ppc, eval=FALSE}
# Standard PPC: density overlay
pp_check(fit)

# Additional checks — run interactively as needed:
# pp_check(fit, type = "stat", stat = "mean")
# pp_check(fit, type = "stat_2d", stat = c("mean", "sd"))
# pp_check(fit, type = "scatter_avg")
```

::: {.callout-note}
**Learn mode — what to look for:**
The dark line shows the distribution of your observed data. The light
blue lines show simulated datasets from your posterior. If the dark
line lies within the cloud of light lines, your model is capturing
the data distribution well. Systematic deviations (e.g., the dark
line peaking higher or lower than the cloud) indicate model
misspecification. See Gelman et al. (2020) Section 6 for guidance
on interpreting PPC plots.

**Posit Assistant:** Ask "What does it mean if my PPC density plot
shows the observed data consistently higher than the posterior
predictive draws?" for a Socratic explanation.
:::

## Family-specific PPC checks

```{r family-ppc, eval=FALSE}
# The diagnostic registry recorded family-specific warnings in Phase 4.
# Review them here:
if (length(wf$diagnostics$family_checks$warnings) > 0) {
  cat("Family-specific warnings from Phase 4:\n")
  for (w in wf$diagnostics$family_checks$warnings)
    cat(" *", w, "\n")
}
```

## Update workflow state

```{r update-wf, eval=FALSE}
wf$ppc_complete <- TRUE
export_context(wf)
saveRDS(wf, "wf_phase5.rds")
cat("Phase 5 complete. wf saved to wf_phase5.rds\n")
cat("Proceed to templates/phase6_loo.qmd\n")
```
