---
title: "RBayesflow Phase 4: MCMC Diagnostics"
format: html
params:
  mode: "learn"
  stage: "explore"
---

<!--
# POSIT ASSISTANT CONTEXT
# This is Phase 4 of the RBayesflow Bayesian workflow.
# Current mode: set by params$mode | Current stage: set by params$stage
# Read wf_context.json in the project root for full workflow state.
# Do NOT suggest running any code directly. Always present suggestions
# as non-executable previews.
# CRITICAL: Do not display coefficient summaries unless
# wf_state$diagnostics$passed == TRUE AND
# wf_state$diagnostics$acknowledged == TRUE.
# If diagnostics failed, suggest diagnostic investigation only.
-->

## Setup

```{r setup, message=FALSE}
source("R/source_all.R")
wf  <- readRDS("wf_phase3.rds")
fit <- readRDS("fit.rds")
```

## Phase 4: MCMC Diagnostics

Run diagnostics on your fitted model.

```{r run-diagnostics, eval=FALSE}
wf <- run_diagnostics(fit, wf)
print(wf)
```

## Diagnostic Review

::: {.callout-warning}
**Interactive step required — run in Console, not by rendering.**

If `print(wf)` above showed a DIAGNOSTIC FAILURE message, run
the chunk below in your RStudio Console (not here):

```r
wf <- wf$diagnose()
```

This will display diagnostic plots and ask you to acknowledge the
failure. Only after acknowledgment will coefficient output be shown.
The `wf$diagnose()` function uses `readline()` which requires an
interactive session — it cannot run inside a rendered document.
:::

```{r diagnose-console, eval=FALSE}
# Run this in your RStudio Console if diagnostics failed:
# wf <- wf$diagnose()
# Then return here and run print(wf) again.
```

## Parameterization Check

```{r param-check, eval=FALSE}
cat("Parameterization:", wf$parameterization, "\n")
if (!is.na(wf$parameterization) &&
    wf$parameterization == "centered" &&
    wf$diagnostics$n_divergences > 0) {
  cat("Tip: Divergences detected with centered parameterization.\n")
  cat("Consider: result_nc <- refit_noncentered(wf, fit)\n")
}
```

## Save workflow state

```{r save-wf, eval=FALSE}
saveRDS(wf, "wf_phase4.rds")
cat("Phase 4 complete. wf saved to wf_phase4.rds\n")
cat("Proceed to templates/phase5_ppc.qmd\n")
```
